Capstone Movielens Report

### 2025-11-02 reports/capstone-movielens.site/05.appendix.Rmd
Report layout: minor fix.
RMSE.Total_kable function: hotfix.

The table created by the internally called [knitr::kable()]().

@@

Prints the final _RMSEs Result Tibble_.

@@

>>>>

The table created by the internally called [knitr::kable()](https://www.rdocumentation.org/packages/knitr/versions/1.43/topics/kable).

@@

Prints the _Final RMSEs Result Tibble_.

@@

It is assumed that the  _Final RMSEs Result Tibble_ is previously constructed from the original _RMSEs Result Tibble_ using the [RMSEs.AddDiffColumn](#func.RMSEs.AddDiffColumn) function described above.
